Simple Type Theory is not too Simple

### 2021-04-07 article.tex
A section about Isabelle from Larry

>>>>

\section{Isabelle/HOL, Simple Type Theory and Locales}
\label{sec:isabelle}

Isabelle/HOL is a proof assistant for higher-order logic: Church's simple type theory~\cite{church40}, with a number of modest extensions. It is therefore based on the typed $\lambda$-calculus with boolean and function types. A boolean-valued function is a predicate, which yields a simple typed set theory that is expressive enough to express abstract mathematics, as we shall see below.

In Church's original conception, the sole purpose to types is to prevent inconsistency. People today, influenced by programming languages, prefer to give types a more dominant role.
